Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding

### 2018-06-20 chapters/introduction/introduction.tex
first paragraph

%\begin{chapquote}{Walt Disney}
  %``Of all of our inventions for mass communication, pictures still
  %speak the most universally understood language.''
%\end{chapquote}

%%Outline:
%\begin{itemize}
  %\item sliver bullet and ``summer project'' story
  %\item \st{Geometry is important.}
  %\item \st{traditional method for geometry detection}
  %\item \st{deep learning (gamer changer)}
  %\item \st{geometry detection with deep learning}
  %\item \st{geometry for deep learning training}
  %\item \st{overhead images}
%\end{itemize}

The study of understanding images has been around for half a century.
A well known anecdote in computer vision community happened in 1960s,
when the MIT professor Dr. Marvin Minsky assigned a summer programming
project to his undergraduates, to recognize objects in a
scene~\cite{boden2006mind}. 
%
Similar to the story of the famous ``Four Color Conjecture'', where
one of the world's renowned mathematicians Dr. Hermann Minkowski
claimed in his class that he was able to solve it before the class
ends.  
However, Not until one hundred years later since it was first
proposed, the ``Four Color Conjecture'' has been stamped as theorem by
the continuous efforts of several generations of talented
mathematicians.  While on the other side, Dr. Marvin Minsky's summer
program still remains open.

It is not a trivial task for machines to understand images in general.
To achieve this goal, researchers adopt a divide-and-conquer strategy,
that is dividing image understanding into various sub-problems like
object recognition, semantic segmentation, and pose estimation \etc.
During past decades, a lot of methods are developed to solve
these
sub-problems. Many of them adopted a bottom-up (\todo{citations})
workflow, where basic level cues play important roles
(\todo{examples}). Among these basic cues, camera geometry is
particularly useful for some computer vision tasks like facade
detection, indoor layout estimation~\cite{ren2016coarse}.

>>>>

\begin{chapquote}{Alan Turing}
  ``I propose to consider the question: Can machine think?''
\end{chapquote}

Before the father of computer asked this question, creating
machines that can think as human has been a dream through the human
history. In the late 18th century, Hungarian inventor, Wolfgan von
Kempelen, constructed an automatic machine called ``The Turk'' (also
known as the ``Mechanical Turk'') to play a chess game. Though it
proved to be an elaborate hoax, people's enthusiasm for machine
intelligence lasts till today. As one of the core elements of
intelligence, human vision plays an important role in our daily lives.
In order to make computer understand images, scholars had put a lot of
research efforts in the study of computer vision. In 1960s, MIT
professor Dr. Marvin Minsky asked his undergraduates to develop
programs that can recognize objects from a scene in their summer
project~\cite{boden2006mind}. Half a century has passed, the question
of this ``summer project'' still remains open.

Understanding images is not trivial for machines.  To achieve this
goal, researchers adopt a divide-and-conquer strategy, that is
dividing image understanding into various sub-problems like object
recognition, semantic segmentation, and pose estimation \etc.  During
past decades, a lot of methods are developed to solve these
sub-problems. Many of them adopted a bottom-up (\todo{citations})
workflow, where basic level cues play important roles
(\todo{examples}). Among these basic cues, camera geometry is
particularly useful for some computer vision tasks like facade
detection, indoor layout estimation~\cite{ren2016coarse}.

### 2018-06-20 chapters/introduction/junk.tex
first paragraph

>>>>

The study of understanding images has been around for half a century.
A well known anecdote in computer vision community happened in 1960s,
when the MIT professor Dr. Marvin Minsky assigned a summer programming
project to his undergraduates, to recognize objects in a
scene~\cite{boden2006mind}. 
%
Similar to the story of the famous ``Four Color Conjecture'', where
one of the world's renowned mathematicians Dr. Hermann Minkowski
claimed in his class that he was able to solve it before the class
ends.  
However, Not until one hundred years later since it was first
proposed, the ``Four Color Conjecture'' has been stamped as theorem by
the continuous efforts of several generations of talented
mathematicians.  While on the other side, Dr. Marvin Minsky's summer
program still remains open.
